---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please always edit the .Rmd file (and generate the .md file from it) -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center", 
  out.width = "600px"
)

# URLs: ------ 

# unikn:
url_unikn <- "https://www.uni-konstanz.de/"

url_unikn_cran   <- "https://CRAN.R-project.org/package=unikn"
url_unikn_github <- "https://github.com/hneth/unikn"

# unicol: 
url_unicol_cran   <- "" # "https://CRAN.R-project.org/package=unicol"
url_unicol_github <- "https://github.com/hneth/unicol"
```


# unicol `r getNamespaceVersion("unicol")` 

<!-- badges: start -->
<!-- badges: end -->

<!-- unicol pkg logo and link: -->
<a href = "`r url_unicol_github`">
<img src = "./inst/pix/pkg_unicol.png" alt = "unicol::" align = "right" width = "220px" style = "width: 220px; float: right; border:0;"/>
</a>

<!-- Slogan: -->

The colors of your university.


## Objectives 

<!-- Goal: -->

The R\ package **unicol** contains colors and color palettes for various universities. 
Our goal is to collect and provide as many palettes as possible for creating scientific visualizations. 

<!-- Course coordinates: --> 

The **unicol** package was developed as a collaborative project by the following course:

* **Open Source Software Development in R** (ADILT applications, PSY-18040), at **[University of Konstanz](https://www.uni-konstanz.de/en/)**   
* Spring 2023: **Tuesdays**, **13:30-15:00**; in **C426** 
* Taught by **[Hansjörg Neth](https://neth.de/)** (<h.neth@uni.kn>, [SPDS](https://www.spds.uni-konstanz.de/), [University of Konstanz](https://www.uni-konstanz.de/en/))


<!-- Relation to unikn:: -->

<!-- unikn pkg logo and link: -->
<!-- <a href = "`r url_unikn_cran`"> -->
<!-- <img src = "./inst/pix/pkg_unikn.png" alt = "unikn::" align = "right" width = "140px" style = "width: 140px; float: right; border:0;"/> -->
<!-- </a> -->

This package is based on the R\ package **[unikn](https://CRAN.R-project.org/package=unikn)** and loads key functionality from it. 


## Installation

You can install the development version of **unicol** from [GitHub](https://github.com/) with:

```{r install-from-github, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hneth/unicol")
```


## Usage

The **unicol** package provides colors and color palettes, whereas the **[unikn](https://CRAN.R-project.org/package=unikn)** package provides color-related functions:

```{r load-pkgs, message = FALSE}
library(unicol)  # for color palettes
library(unikn)   # for color functions
```


## Contents

```{r unicol-stats, echo = FALSE}
n_pals <- length(unique(unicol_data$pal))
n_inst <- length(unique(unicol_data$inst))
```

The **unicol** package currently provides **`r n_pals`\ color palettes** from **`r n_inst`\ institutions**. 

<!-- **Table\ 1** provides an overview of all color palettes:  -->

```{r unicol-pals-table-all, echo = FALSE, eval = FALSE}
# Data:
all_pals_df <- unicol_data
names(all_pals_df) <- c("Institution", "(aka.)", "URL", "Palette name")

tab_caption <- paste0("Overview of ", n_pals, " unicol palettes (from ", n_inst, " institutions).")

# Print table:
knitr::kable(all_pals_df, caption = tab_caption, row.names = TRUE)
```

(See the vignette on **Color palettes** for an overview of all colors and institutions.)


## Examples 

<!-- Goal: Show some color palettes and how they can be used: -->


### Color palettes

<!-- The **unicol** package currently contains **`r n_pals`\ color palettes** from **`r n_inst`\ institutions**.  -->

<!-- Example 1: Random pals (from vignette color_pals.Rmd): -->

```{r unicol-pals-example-1-parameters, echo = FALSE, eval = TRUE}
# Parameters:
N <- length(unicol_data$pal)
n <- 50 # N
```

```{r unicol-pals-example-1-lists, echo = FALSE, eval = TRUE}
set.seed(77) # 77 102 123  # reproducible randomness

# A: Get sample_n of my_pals from all unicol_data$pal:
sample_n <- sort(sample(x = 1:N, size = n, replace = FALSE))
my_pals <- unicol_data$pal[sample_n]

# B: Get sample_n of primary_pals:
is_pal_1 <- grepl(pattern = "_1", unicol_data$pal)
# sum(is_pal_1)
primary_pals <- unicol_data$pal[is_pal_1]

N <- length(primary_pals)
sample_n <- sort(sample(x = 1:N, size = n, replace = FALSE))
my_pals <- primary_pals[sample_n]


# Initialize data structures:
pal_list  <- vector(mode = "list", length = n)
pal_names <- vector(mode = "character", length = n)
col_count <- 0

# Loop: Iterate through n palettes:
for (i in 1:n){
  
  cur_name  <- my_pals[i]
  cur_pal   <- get(cur_name)
  cur_count <- length(cur_pal)
    
  pal_list[[i]] <- cur_pal
  pal_names[i]  <- cur_name
  col_count     <- col_count + cur_count
    
} # for i loop end.

# Check:
# pal_list
# pal_names

# Captions:
tab_caption <- paste0("A sample of ", n, " unicol palettes (containing ", col_count, " colors).")
fig_caption <- paste0("Figure 1: A sample of ", n, " unicol palettes (containing ", col_count, " colors).")
my_main     <- paste0("Illustrating ", n, " unicol palettes (with ", col_count, " colors)")
```

```{r unicol-pals-example-1-stats, echo = FALSE, eval = FALSE}
# Stats (for n <- N):
n_pals  # number of color palettes: 202 on 2023-04-08. 
n_inst  # number of institutions: 86 on 2023-08-03.
# Colors:
length(unlist(pal_list))          # number of colors: 1327 on 2023-04-08. 
length(unique(unlist(pal_list)))  # number of unique colors: 1130 on 2023-04-08. 
```

<!-- As a table: -->

```{r unicol-pals-example-1-table, echo = FALSE, eval = FALSE}
knitr::kable(unicol_data[sample_n, ], caption = tab_caption)
```

<!-- As a figure: -->

**Figure\ 1** illustrates `r n` random color palettes (with `r col_count`\ colors): 

```{r unicol-pals-example-1-figure, echo = FALSE, eval = TRUE, fig.width = 8, out.width = "90%", fig.align = 'center', fig.asp = 1.5, fig.cap = fig_caption}
# Figure: Illustrate color palettes:
unikn::seecol(pal = pal_list,
              pal_names = pal_names,         
              main = my_main)
```


### Using color palettes

As the **unicol** palettes are provided as vectors of R colors, they can simply be used as the `col` argument of R graphics functions. 
For instance, we can use the MIT colors (of the [Massachusetts Institute of Technology](https://web.mit.edu/)) in a bar plot as follows:

```{r example-base-r-1}
barplot(height = 1:10, 
        col = mit_pal, 
        main = "Using the MIT colors")
```

To modify a color palette (e.g., by resizing or adding transparency), we can use the `usecol()` function of the 
**[unikn](https://CRAN.R-project.org/package=unikn)** package:

```{r example-base-r-2}
barplot(height = 1:10, 
        col = usecol(mit_pal, n = 10), 
        main = "Using a gradient of MIT colors")
```

<!-- More examples: -->

Here are some some additional examples how the color palettes from **unicol** can be used:

```{r examples-unicol, message = FALSE}
seecol(yale_1, main = "The primary colors of Yale University")
demopal(berkeley_1, type = 2, main = "The colors of Berkeley, University of California", seed = 3)
demopal(limerick_1, type = 3, main = "Using the colors of Limerick University")
```

<!-- +++ here now +++  -->


<!-- unicol pkg logo and link: -->
<a href = "`r url_unicol_github`">
<img src = "./inst/pix/pkg_unicol.png" alt = "unicol::" align = "right" width = "220px" style = "width: 220px; float: right; border:0;"/>
</a>


## Contact

Add contact details here.


------


<!-- Footer: -->

[File `README.Rmd` updated on `r Sys.Date()`.]

<!-- eof. --> 
