---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please always edit the .Rmd file (and generate the .md file from it) -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center", 
  out.width = "600px"
)
```

# unicol

<!-- badges: start -->
<!-- badges: end -->

The colors of your university.


## Goal

The R package **unicol** provides colors and color palettes for various universities. 

<!-- Course coordinates: --> 

The **unicol** package was developed as a collaborative project by the following course:

* **Open Source Software Development in R** (ADILT applications, PSY-18040), at **[University of Konstanz](https://www.uni-konstanz.de/en/)**   
* Spring 2023: **Tuesdays**, **13:30-15:00**; in **C426** 
* Taught by **[Hansjörg Neth](https://neth.de/)** (<h.neth@uni.kn>, [SPDS](https://www.spds.uni-konstanz.de/), [University of Konstanz](https://www.uni-konstanz.de/en/))


<!-- Goal: -->

The goal of **unicol** is to provide university color palettes for creating scientific visualizations. 

This package is based on the R\ package **[unikn](https://CRAN.R-project.org/package=unikn)** and loads key functionality from it. 


## Installation

You can install the development version of **unicol** from [GitHub](https://github.com/) with:

```{r install-from-github, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hneth/unicol")
```


## Usage

The **unicol** package provides colors and color palettes, whereas the **[unikn](https://CRAN.R-project.org/package=unikn)** provides color-related functions:

```{r load-pkgs, message = FALSE}
library(unicol)  # for color palettes
library(unikn)   # for color functions
```

## Contents

<!-- A list of all unicol palettes: -->

```{r list-all-pals, echo = FALSE}
# ToDo: Get from palette registry data: ----

# Create a list of all unicol color palettes:
all_unicol_pals <- list(caltech_pal_1, caltech_pal_2, caltech_pal_3,
                        eth_pal_1, eth_pal_2, eth_pal_3, 
                        fu_pal_1, fu_pal_2, fu_pal_3,
                        hu_pal_1, hu_pal_2,
                        lmu_pal_1, lmu_pal_2, lmu_pal_3,
                        mit_pal,
                        mpg_pal,
                        nyu_1, nyu_2, nyu_accent, nyu_neutral,
                        rpi_pal_1, rpi_pal_2, rpi_pal_3,
                        # etc.
                        uni_stanford_1, # uni_stanford_accent, 
                        uni_stanford_web
                        )

all_cols <- unlist(all_unicol_pals)

# Can we get all palette names (as a character vector)?

# names(all_unicol_pals) # does not work

# deparse(substitute()) # gets an object's name
# 
# get_name <- function(x){
#  
#  deparse(substitute(x))
#  
# }
#
# lapply(all_unicol_pals, get_name)

# Manually:
all_unicol_pal_names <- c("caltech_pal_1", "caltech_pal_2", "caltech_pal_3",
                          "eth_pal_1", "eth_pal_2", "eth_pal_3", 
                          "fu_pal_1", "fu_pal_2", "fu_pal_3",
                          "hu_pal_1", "hu_pal_2",
                          "lmu_pal_1", "lmu_pal_2", "lmu_pal_3",
                          "mit_pal",
                          "mpg_pal",
                          "nyu_1", "nyu_2", "nyu_accent", "nyu_neutral",
                          "rpi_pal_1", "rpi_pal_2", "rpi_pal_3",
                          # etc.
                          "uni_stanford_1", # "uni_stanford_accent", 
                          "uni_stanford_web"
)


# Check:
# length(all_unicol_pals) == length(all_unicol_pal_names)

# Statistics: ---- 
n_pals <- length(all_unicol_pals)
n_cols <- length(all_cols)
```


The **unicol** package currently contains `r n_pals`\ color palettes (with a total of `r n_cols`\ colors) from Z\ institutions. 


An overview of the current color palettes provided by the **unicol** package:

```{r show-contents, echo = FALSE, fig.asp = 1}
seecol(all_unicol_pals, 
       pal_names = all_unicol_pal_names, 
       main = "The unicol color palettes")
```


## Examples 

Here are some examples how the color palettes from **unicol** can be used:

```{r examples, message = FALSE}
seecol(uni_yale_primary, main = "Primary colors of Yale University")
demopal(uni_berkeley_primary_1, type = 2, main = "Using the colors of Uni Berkeley")
demopal(nyu_1, type = 3, main = "NYU colors")
```


------

<!-- Footer: -->

[File `README.Rmd` updated on `r Sys.Date()`.]


<!-- eof. --> 
