---
title: "Color palettes"
author: "Hansjoerg Neth"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    fig_caption: yes
vignette: > 
  %\VignetteIndexEntry{Color palettes}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
options(max.print = "75")

knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      prompt = FALSE,
                      tidy = FALSE,
                      collapse = TRUE, 
                      comment = "#>",
                      message = FALSE,
                      warning = FALSE,
                      # Default figure options:
                      # fig.width = 6, 
                      # fig.asp = .80 # .618, # golden ratio
                      fig.align = "center",
                      out.width = "60%"
)

# URLs: ------ 

# unikn:
url_unikn <- "https://www.uni-konstanz.de/"

url_unikn_cran   <- "https://CRAN.R-project.org/package=unikn"
url_unikn_github <- "https://github.com/hneth/unikn"

# unicol: 
url_unicol_cran   <- "" # "https://CRAN.R-project.org/package=unicol"
url_unicol_github <- "https://github.com/hneth/unicol"
```

<!-- unikn logo and link: -->
<!-- <a href = "`r url_unikn`"> -->
<!-- <img src = "../inst/pix/logo_unikn.png" alt = "unikn::" align = "right" width = "300px" style = "width: 300px; float: right; border:0;"/> -->
<!-- </a> -->

<!-- unikn pkg logo and link: -->
<!-- <a href = "`r url_unikn_cran`"> -->
<!-- <img src = "../inst/pix/pkg_unikn.png" alt = "unikn::" align = "right" width = "140px" style = "width: 140px; float: right; border:0;"/> -->
<!-- </a> -->

<!-- unicol pkg logo and link: -->
<a href = "`r url_unicol_github`">
<img src = "../inst/pix/pkg_unicol.png" alt = "unicol::" align = "right" width = "220px" style = "width: 220px; float: right; border:0;"/>
</a>

This vignettes provides an overview of the **color palettes** provided by the **unicol** package. 
(See the vignette on [Using color palettes](using_pals.html) for how to use the **unicol** color palettes.) 

We install or load the **unicol** package to get started: 

```{r load-unicol-pkg, message = FALSE, warning = FALSE}
# install.packages('unicol')  # install unicol from CRAN client
library('unicol')             # load the package
```


## The color palettes of the **unicol** package

```{r unicol-stats, echo = FALSE}
n_pals <- length(unique(unicol_data$pal))
n_inst <- length(unique(unicol_data$inst))
```

The **unicol** package currently provides **`r n_pals`\ color palettes** from **`r n_inst`\ institutions**. 


### Illustration 

```{r unicol-pals-example, echo = FALSE, eval = TRUE}
# Parameters:
N <- length(unicol_data$pal)
n <- 50 # N

set.seed(102) # 77 102 123  # reproducible randomness

# A: Get sample_n of my_pals from all unicol_data$pal:
sample_n <- sort(sample(x = 1:N, size = n, replace = FALSE))
my_pals <- unicol_data$pal[sample_n]

# B: Get sample_n of primary_pals:
is_pal_1 <- grepl(pattern = "_1", unicol_data$pal)
# sum(is_pal_1)
primary_pals <- unicol_data$pal[is_pal_1]

N <- length(primary_pals)
sample_n <- sort(sample(x = 1:N, size = n, replace = FALSE))
my_pals <- primary_pals[sample_n]

# Initialize data structures:
pal_list  <- vector(mode = "list", length = n)
pal_names <- vector(mode = "character", length = n)
col_count <- 0

# Loop: Iterate through n palettes:
for (i in 1:n){
  
  cur_name  <- my_pals[i]
  cur_pal   <- get(cur_name)
  cur_count <- length(cur_pal)
    
  pal_list[[i]] <- cur_pal
  pal_names[i]  <- cur_name
  col_count     <- col_count + cur_count
    
} # for i loop end.

# Check:
# pal_list
# pal_names

# Captions:
tab_caption <- paste0("A sample of ", n, " unicol palettes (containing ", col_count, " colors).")
fig_caption <- paste0("Figure 1: A sample of ", n, " unicol palettes (containing ", col_count, " colors).")
my_main     <- paste0("Illustrating ", n, " unicol palettes (with ", col_count, " colors)")
```

```{r unicol-pals-example-stats, echo = FALSE, eval = FALSE}
# Stats (for n <- N):
n_pals  # number of color palettes: 202 on 2023-04-08. 
n_inst  # number of institutions: 86 on 2023-08-03.
# Colors:
length(unlist(pal_list))          # number of colors: 1327 on 2023-04-08. 
length(unique(unlist(pal_list)))  # number of unique colors: 1130 on 2023-04-08. 
```


<!-- Show as table: -->

```{r unicol-pals-table-sample, echo = FALSE, eval = FALSE}
knitr::kable(unicol_data[sample_n, ], caption = tab_caption)
```


<!-- Show as figure: -->

**Figure\ 1** illustrates `r n` random color palettes: 

```{r unicol-pals-figure-sample, echo = FALSE, eval = TRUE, fig.width = 8, out.width = "90%", fig.asp = 1.5, fig.cap = fig_caption}
# Figure: Illustrate color palettes:
unikn::seecol(pal = pal_list,
              pal_names = pal_names,         
              main = my_main)
```


### Overview

**Table\ 1** provides an overview of **all `r n_pals`\ color palettes** from from **`r n_inst`\ institutions**: 

```{r unicol-pals-table-all, echo = FALSE, eval = TRUE}
# Data:
all_pals_df <- unicol_data
names(all_pals_df) <- c("Institution", "(aka.)", "URL", "Palette name")

tab_caption <- paste0("Overview of ", n_pals, " unicol palettes (from ", n_inst, " institutions).")

# Print table:
knitr::kable(all_pals_df, caption = tab_caption, row.names = TRUE)
```


<!-- +++ here now +++  -->


## Vignettes

<!-- unicol pkg logo and link: -->
<a href = "`r url_unicol_github`">
<img src = "../inst/pix/pkg_unicol.png" alt = "unicol::" align = "right" width = "220px" style = "width: 220px; float: right; border:0;"/>
</a>

The following vignettes provide an overview of and examples for using the **unicol** color palettes: 

<!-- Table of vignettes: -->

| Nr.  | Vignette | Content    |        
| ---: |:---------|:-----------|
| 1. | [Color palettes](color_pals.html) | The color palettes of the **unicol** R package |
| 2. | [Using color palettes](using_pals.html) | Recipes for using the **unicol** color palettes |

<!-- eof. -->